Uniform sampling across the whole territory without any cells

### 2024-08-27 First_steps/No_tree_no_grid.Rmd
No_tree with tables

```{r}
library(readxl) # to read the initial file
library(magrittr) # for pipes
library(tibble) # for add_column and tibble
```

@@

@@

```{r}
# f_ind(x,y)^2 = f_ind(x,y)
varTHEO_x <- val_x2/p - (1/n)*(val_x^2)
# Theoretical variance: 8.333333e+13, i.e. around 8.341029e+13
# Close to the estimated one
```

@@

```{r}
res <- true_vs_MC(n = 1000, B = 1000, f = f_1)
cat("True integral:", 1e+06, "\nMean of all the estimations:", res[1])
cat("\n\nTheoretical variance:", varTHEO_area, "\nMonte-Carlo variance:", res[2])
# Totals: 1e+06 and 1e+06 (Equality as always)
# Variances: 0 and 0 (Equality as always)
```

```{r}
res <- true_vs_MC(n = 1000, B = 1000, f = f_ind)
cat("True integral:", 500000, "\nMean of all the estimations:", res[1])
cat("\n\nTheoretical variance:", varTHEO_ind, "\nMonte-Carlo variance:", res[2])
# Ex:
# True integral: 5e+05 
# Mean of all the estimations: 499214

@@

```{r}
res <- true_vs_MC(n = 1000, B = 1000, f = f_x)
cat("True integral:", 5e+08, "\nMean of all the estimations:", res[1])
cat("\n\nTheoretical variance:", varTHEO_x, "\nMonte-Carlo variance:", res[2])
# Ex:
# True integral: 5e+08 
# Mean of all the estimations: 499874718

# Theoretical variance: 8.333333e+13 
# Monte-Carlo variance: 7.99389e+13
```

>>>>

```{r}
install.packages("kableExtra")
```

```{r}
library(readxl) # to read the initial file
library(magrittr) # for pipes
library(tibble) # for add_column and tibble
library(kableExtra) # To have LaTeX tables based on dataframes
```

@@

$V[\hat{\tau}_{y\pi}(S)] = \frac{n}{A} \times \frac{A}{2} - \frac{1}{n} \times (\frac{A}{2})^{2} $

@@

```{r}
varTHEO_x <- val_x2/p - (1/n)*(val_x^2)
# Theoretical variance: 8.333333e+13, i.e. around 8.341029e+13
# Close to the estimated one
```

@@

```{r}
res1 <- true_vs_MC(n = 1000, B = 1000, f = f_1)
cat("True integral:", 1e+06, "\nMean of all the estimations:", res1[1])
cat("\n\nTheoretical variance:", varTHEO_area, "\nMonte-Carlo variance:", res1[2])
# Totals: 1e+06 and 1e+06 (Equality as always)
# Variances: 0 and 0 (Equality as always)
```

```{r}
res2 <- true_vs_MC(n = 1000, B = 1000, f = f_ind)
cat("True integral:", 500000, "\nMean of all the estimations:", res2[1])
cat("\n\nTheoretical variance:", varTHEO_ind, "\nMonte-Carlo variance:", res2[2])
# Ex:
# True integral: 5e+05 
# Mean of all the estimations: 499214

@@

```{r}
res3 <- true_vs_MC(n = 1000, B = 1000, f = f_x)
cat("True integral:", 5e+08, "\nMean of all the estimations:", res3[1])
cat("\n\nTheoretical variance:", varTHEO_x, "\nMonte-Carlo variance:", res3[2])
# Ex:
# True integral: 5e+08 
# Mean of all the estimations: 499874718

# Theoretical variance: 8.333333e+13 
# Monte-Carlo variance: 7.99389e+13
```
# Nice table

```{r}
# Theoretical variances and values
VAR_theo <- c(varTHEO_area, varTHEO_ind, varTHEO_x)
VAL_theo <- c(area, half_area, val_x)
THEO_df <- as.data.frame(cbind(VAL_theo, VAR_theo))
```

```{r}
RES_df <- as.data.frame(rbind(res1,res2,res3))
```

```{r}
# `Parameter of interest` = fct_names,

# Table for comparison
diff_var <- data.frame(`Difference between totals` = paste0(round(mapply(function(x,y){unlist(100*(max(x,y)-min(x,y))/min(x, y))}, unlist(THEO_df[1]), unlist(RES_df[1])), digits = 3), "%"), `Difference between variances` = paste0(round(mapply(function(x,y){100*(max(x,y)-min(x,y))/min(x,y)}, unlist(THEO_df[2]), unlist(RES_df[2])), digits = 3), "%") )
# diff_var <- ifelse(diff_var == "NaN%", 0, diff_var)
diff_var[diff_var == "NaN%"] <- "0%"
```

```{r}
tab_var <- diff_var %>%
  kable("latex", booktabs = FALSE, align = "cc", linesep = c("", "", "",
  "\\addlinespace"), caption = paste("Assessment of the efficiency with samples with size 1000 and 1000 Monte Carlo iterations"), col.names = gsub("[.]", " ", names(diff_var))) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  collapse_rows(columns = 1, latex_hline = "major")
```

```{r}
# The table itself
tab_var
```

```{r}
# The code that produced the table
cat(tab_var)
```
